**Selective DNA and Protein Isolation from Marine Macrophyte Surfaces**

### 2020-11-20 submission/manuscript.Rmd
References customization.
Formatting text.
Units format.

### Protein isolation
Proteins were isolated according to the protocol for protein isolation from soil described in @Chourey2010 and modified by @Hultman2015. This protocol was further modified and adapted for microbial protein isolation from macrophyte surfaces as described below. Twenty (20) \si{\ml} of protein extraction buffer (4 \si{\percent} SDS, 100 \si{\milli\Molar} Tris-HCl [pH 8.0]) was added to 5 \si{\g} wet weight of leaves or 10 \si{\g} wet weight of thalli. The mixture was incubated in boiling water for 5 \si{\minute}, vortexed for 10 \si{\minute} and incubated again in boiling water for 5 \si{\minute}. After a brief vortex, the lysate was transferred to a clean tube separating the host leaves or thalli from the mixture containing lysed epiphytic cells. Dithiothreitol (DTT; final concentration 24 \si{\milli\Molar}) was added and proteins were precipitated with chilled 100 \si{\percent} trichloroacetic acid (TCA; final concentration 20 \si{\percent}) overnight at \num{-20} °C. Precipitated proteins were centrifuged at 10,000 × g and 4 \si{\degreeCelsius} for 40 \si{\minute}. The obtained protein pellet was washed three times with chilled acetone. During the first washing step the pellet was transferred to a clean 1.5 \si{\ml} tube. After each washing step, samples were centrifuged at 20,000 × g and 4 \si{\degreeCelsius} for 5 \si{\minute}. Dried pellets were stored at \num{-80} °C until further analysis.

@@

\newpage
## References
<div id="refs"></div>

@@

## Figure Captions
**\autoref{confocal_december}.** \nameref{confocal_december}

>>>>

### Protein isolation
Proteins were isolated according to the protocol for protein isolation from soil described in @Chourey2010 and modified by @Hultman2015. This protocol was further modified and adapted for microbial protein isolation from macrophyte surfaces as described below. Twenty (20) \si{\ml} of protein extraction buffer (4 \si{\percent} SDS, 100 \si{\milli\Molar} Tris-HCl [pH 8.0]) was added to 5 \si{\g} wet weight of leaves or 10 \si{\g} wet weight of thalli. The mixture was incubated in boiling water for 5 \si{\minute}, vortexed for 10 \si{\minute} and incubated again in boiling water for 5 \si{\minute}. After a brief vortex, the lysate was transferred to a clean tube separating the host leaves or thalli from the mixture containing lysed epiphytic cells. Dithiothreitol (DTT; final concentration 24 \si{\milli\Molar}) was added and proteins were precipitated with chilled 100 \si{\percent} trichloroacetic acid (TCA; final concentration 20 \si{\percent}) overnight at \num{-20} \si{\degreeCelsius}. Precipitated proteins were centrifuged at 10,000 × g and 4 \si{\degreeCelsius} for 40 \si{\minute}. The obtained protein pellet was washed three times with chilled acetone. During the first washing step the pellet was transferred to a clean 1.5 \si{\ml} tube. After each washing step, samples were centrifuged at 20,000 × g and 4 \si{\degreeCelsius} for 5 \si{\minute}. Dried pellets were stored at \num{-80} \si{\degreeCelsius} until further analysis.

@@

\newpage
## References
\interlinepenalty=10000
\setlength{\emergencystretch}{3.5em}
<div id="refs"></div>

@@

## Figure captions
**\autoref{confocal_december}.** \nameref{confocal_december}
